From Freebase to Wikidata: The Great Migration

### 2015-10-06 paper.tex
Use pdf for facts-topic-mapping file
Converts Wikidata-statement image to PDF

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/Wikidata-statement.png}
\caption{\todo{Get PDF version} An example of Wikidata statement (from
	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
\label{fig:statement}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/facts-topics-mapping.png}
\caption{Number of mapped and not mapped topics with more than x facts.
Note the log scale on both axis.}
\end{figure}

>>>>

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/Wikidata_statement.pdf}
\caption{An example of Wikidata statement (from
	\url{https://commons.wikimedia.org/wiki/File:Wikidata_statement.svg})}
\label{fig:statement}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=8.45 cm]{img/facts-topics-mapping.pdf}
\caption{Number of mapped and not mapped topics with more than x facts.
Note the log scale on both axis.}
\end{figure}
